Incentivizing Exploration with Unbiased History

### 2018-11-02 intro.tex
OK some more of the intro is there.

We measure the machine learning performance of a disclosure policy in terms of \emph{regret}, a standard notion from online machine learning. Regret is defined as the difference in the total expected reward between the best fixed action and actions induced by the policy.

\xhdr{Our results.}
We design transitive unbiased-subhistory policies with near-optimal regret.

@@

\xhdr{Related work.}

\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.

>>>>

\xhdr{Regret.} We measure the performance of a disclosure policy in terms of \emph{regret}, a standard notion from the literature on multi-armed bandits. Regret is defined as the difference in the total expected reward between the best fixed action and actions induced by the policy. Regret is typically studied as a function of the time horizon $T$, which in our model is the number of agents. For multi-armed bandits, $o(T)$ regret bounds are deemed non-trivial, and $O(\sqrt{T})$ regret bounds are optimal in the worst case. Regret bounds that depend on a particular problem instance are also considered. A crucial parameter then is the \emph{gap} $\Delta$, the difference between the best and second best expected reward. One can achieve $O(\tfrac{1}{\Delta}\; \log T)$ regret rate, without knowing the $\Delta$.

\xhdr{Our results and discussion.}
Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions. This policy also obtains the optimal instance-dependent regret rate
    $\tilde{O}(\tfrac{1}{\Delta})$
for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance. In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.

The main challenge is that the agents still follow exploitation-only behavior, just like they do for the full-disclosure policy, albeit based only on a portion of history. A disclosure policy controls the flow of information (who sees what), but not the \emph{content} of that information.

The first step is to obtain any substantial improvement over the full-disclosure policy. We accomplish this with a relatively simple policy which runs the full-disclosure policy ``in parallel" on several disjoint subsets of agents,  collects all data from these runs and discloses it to all remaining agents. While any single run of the full-disclosure policy may get stuck on a suboptimal arm, having these parallel runs ensure that sufficiently many of them will ``get lucky" and provide some exploration. This simple policy achieves $\tilde{O}(T^{2/3})$ regret. Conceptually, it implements a basic bandit algorithm that explores uniformly for a pre-set number of rounds, then picks one arm for exploitation and stays with it for the remaining rounds. We think of this policy  as having two ``levels": Level 1 contains the parallel runs, and Level 2 is everything else.

The next step is to implement \emph{adaptive exploration}, when exploration schedule is adapted to previous observations. This is needed to improve over the $\tilde{O}(T^{2/3})$ regret. We upgrade the simple two-level policy with a middle level, where agents receive the data collected in some (but not all) runs from the first level. Essentially, this new level provides exploration only if the gap $\Delta$ is small (and therefore more exploration is needed).

The main result extends this construction to multiple levels, connected in fairly intricate ways. \ascomment{add more}.

@@

\input{related-work}
